\assignment

### 2017-03-22 project/paper.rnw
Just needed to rescale!

\section{Examples}

@@

\subsection{True Log-Linear Intensity Surface}

@@

\subsection{Simple UXO Site}

@@

<<polyfit1, eval = FALSE>>=
ex_fit4 <- ppm(ex_ppp ~ polynom(x, y, 4))
@

\section{Simulation Study}

What to compare? MSPE for this method vs the moving average kriging? I'd
like to cross-validate (could leave one transect out) but I don't know how to
contruct a criterion. Maybe compare modeled intensity within the rectangle to
a kernel intensity estimate?

>>>>

%\section{Examples}

@@

\section{True Log-Linear Intensity Surface}

@@

\section{Simple UXO Site}

@@

<<polyfit1, warning = FALSE, fig.height = 8, fig.pos = 'p', fig.cap = ''>>=
# Create a quadrature scheme manually to ensure there are dummy points on
# each transect.
# TODO: Figure out weights.
ex_Q <- quad(data = ex_ppp,
             dummy = as.ppp(rbind(
               data.frame(vertices(Window(ex_ppp))),
               do.call(rbind, lapply(unique(ex_path$x), function(x){
                 return(data.frame(
                   x = x, y = seq(min(ex_path$y), max(ex_path$y),
                                  length.out = 128)
                 ))}))), W = Window(ex_ppp)))

ex_fit2 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 2), correction = 'iso')
ex_fit3 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 3), correction = 'iso')
ex_fit4 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 4), correction = 'iso')
ex_fit5 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 5), correction = 'iso')
ex_fit6 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 6), correction = 'iso')
ex_fit7 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 7), correction = 'iso')
ex_fit8 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 8), correction = 'iso')
ex_fit9 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 9), correction = 'iso')
ex_fit10 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 10), correction = 'iso')
ex_fit11 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 11), correction = 'iso')
ex_fit12 <- ppm(ex_Q, ~ polynom(scale(x), scale(y), 12), correction = 'iso')

par(mfrow = c(4, 3), mar = c(1, 0, 1.2, 2), las = 2, cex = 1)
plot(predict(ex_fit2, window = site_window), main = '2nd Degree')
plot(predict(ex_fit3, window = site_window), main = '3rd Degree')
plot(predict(ex_fit4, window = site_window), main = '4th Degree')
plot(predict(ex_fit5, window = site_window), main = '5th Degree')
plot(predict(ex_fit6, window = site_window), main = '6th Degree')
plot(predict(ex_fit7, window = site_window), main = '7th Degree')
plot(predict(ex_fit8, window = site_window), main = '8th Degree')
plot(predict(ex_fit9, window = site_window), main = '9th Degree')
plot(predict(ex_fit10, window = site_window), main = '10th Degree')
plot(predict(ex_fit11, window = site_window), main = '11th Degree')
plot(predict(ex_fit12, window = site_window), main = '12th Degree')
# TODO: Kernel density plot.
@
